---
title: "RMarkdownFileFinal"
author: "Anna Greene"
date: "4/28/2022"
output: html_document
---

### Explaination of my functions

```{r}
basicStatsConfirmed <- function(oddish){
  titles <- c("Mean", "Median","Variance", "Min", "Max")
  newDataFrame <- data.frame(1:5, rownames = titles)
  names(newDataFrame)[1] <- "Basic Statistics"
  newDataFrame[1] <- c(mean(oddish), median(oddish), var(oddish), min(oddish), max(oddish))
  newDataFrame
}
```

I created this basic statistics function that shows the mean, median, variance, minimum, and maximum of the confirmed COVID-19 cases in European countries. I named it "Oddish" because that is my favorite Pokemon!

```{r}
basicStatsDeaths <- function(temp){
  titles <- c("Mean", "Median", "Variance", "Min", "Max")
  newDataFrame <- data.frame(1:5, rownames = titles)
  names(newDataFrame)[1] <- "Basic Statistics"
  newDataFrame[1] <- c(mean(temp), median(temp), var(temp), min(temp), max(temp))
  newDataFrame
}
```

This function is similar to the first function and provides the basic statistics. It shows the mean, median, variance, minimum, and maximum deaths of the confirmed cases in European countries. 

```{r}
mybarplotconfirmed <- function(barplot){
  ggplot(Europe_Covid, aes(x = Country.Region, y = Confirmed)) +
  geom_bar(stat = "identity",fill = "#3C963C") +
  coord_flip() +
  theme_bw() +
  labs(x = "Country",
       y = "Confirmed",
       title = "Confirmed Cases in European Countries")
}
```

This function creates a bar graph that shows the European countries on the Y-axis and the number of confirmed COVID-19 cases on the X-axis. This function helps you visualize which countries have many cases and which do not.

```{r}
mybarplotdeaths <- function(barplot2){
  ggplot(Europe_Covid, aes(x = Country.Region, y = Deaths)) +
    geom_bar(stat = "identity",fill = "#3C963C") +
    coord_flip() +
    theme_bw() +
    labs(x = "Country",
         y = "Deaths",
         title = "Deaths of Confirmed Cases in European Countries")
}
```

This function also creates a bar graph that shows the European countries on the Y-axis and the number of deaths of the confirmed cases on the X-axis. This function helps you visulaize which countries had have high death rates and which do not.

```{r}
xysteps <- function(x,y){

  (x/y)

}
```

This function does a calculation and divides the confirmed cases by the deaths. By doing this calculation, we find out that there is a 6% death rate in European countries.
